Appendix C: Latent Class Growth Analysis

### 2023-01-24 appendix_c.tex
revert MGV previous commit

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{df\_scores }\OtherTok{\textless{}{-}}\NormalTok{ df\_plot}
\CommentTok{\# Store original range of SCL}
\NormalTok{rng\_scl }\OtherTok{\textless{}{-}} \FunctionTok{range}\NormalTok{(df\_scores}\SpecialCharTok{$}\NormalTok{scl)}
\CommentTok{\# Log{-}transform}
\NormalTok{df\_scores}\SpecialCharTok{$}\NormalTok{log }\OtherTok{\textless{}{-}}\NormalTok{ scales}\SpecialCharTok{::}\FunctionTok{rescale}\NormalTok{(}\FunctionTok{log}\NormalTok{(df\_scores}\SpecialCharTok{$}\NormalTok{scl), }\AttributeTok{to =} \FunctionTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{1}\NormalTok{))}
\CommentTok{\# Square root transform}
\NormalTok{df\_scores}\SpecialCharTok{$}\NormalTok{sqrt }\OtherTok{\textless{}{-}}\NormalTok{ scales}\SpecialCharTok{::}\FunctionTok{rescale}\NormalTok{(}\FunctionTok{sqrt}\NormalTok{(df\_scores}\SpecialCharTok{$}\NormalTok{scl), }\AttributeTok{to =} \FunctionTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{1}\NormalTok{))}
\CommentTok{\# Cube root transform}
\NormalTok{df\_scores}\SpecialCharTok{$}\NormalTok{qrt }\OtherTok{\textless{}{-}}\NormalTok{ scales}\SpecialCharTok{::}\FunctionTok{rescale}\NormalTok{(df\_scores}\SpecialCharTok{$}\NormalTok{scl}\SpecialCharTok{\^{}}\NormalTok{.}\DecValTok{33}\NormalTok{, }\AttributeTok{to =} \FunctionTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{1}\NormalTok{))}
\CommentTok{\# Reciprocal transform}
\NormalTok{df\_scores}\SpecialCharTok{$}\NormalTok{reciprocal }\OtherTok{\textless{}{-}}\NormalTok{ scales}\SpecialCharTok{::}\FunctionTok{rescale}\NormalTok{(}\DecValTok{1}\SpecialCharTok{/}\NormalTok{df\_scores}\SpecialCharTok{$}\NormalTok{scl, }\AttributeTok{to =} \FunctionTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{1}\NormalTok{))}
\CommentTok{\# Define function for Box{-}Cox transformation}
\NormalTok{bc }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(x, lambda)\{}
\NormalTok{  (((x }\SpecialCharTok{\^{}}\NormalTok{ lambda) }\SpecialCharTok{{-}} \DecValTok{1}\NormalTok{) }\SpecialCharTok{/}\NormalTok{ lambda)}
\NormalTok{\}}
\CommentTok{\# Inverse Box{-}Cox transformation}
\NormalTok{invbc }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(x, lambda)\{}
\NormalTok{  ((x}\SpecialCharTok{*}\NormalTok{lambda)}\SpecialCharTok{+}\DecValTok{1}\NormalTok{)}\SpecialCharTok{\^{}}\NormalTok{(}\DecValTok{1}\SpecialCharTok{/}\NormalTok{lambda)}
\NormalTok{\}}
\CommentTok{\# Box{-}Cox transform}
\NormalTok{b }\OtherTok{\textless{}{-}}\NormalTok{ MASS}\SpecialCharTok{::}\FunctionTok{boxcox}\NormalTok{(}\FunctionTok{lm}\NormalTok{(df\_scores}\SpecialCharTok{$}\NormalTok{scl }\SpecialCharTok{\textasciitilde{}} \DecValTok{1}\NormalTok{), }\AttributeTok{plotit =} \ConstantTok{FALSE}\NormalTok{)}
\NormalTok{lambda }\OtherTok{\textless{}{-}}\NormalTok{ b}\SpecialCharTok{$}\NormalTok{x[}\FunctionTok{which.max}\NormalTok{(b}\SpecialCharTok{$}\NormalTok{y)]}
\NormalTok{df\_scores}\SpecialCharTok{$}\NormalTok{boxcox }\OtherTok{\textless{}{-}} \FunctionTok{bc}\NormalTok{(df\_scores}\SpecialCharTok{$}\NormalTok{scl, lambda)}
\CommentTok{\# Store range of Box{-}Cox transformed data}
\NormalTok{rng\_bc }\OtherTok{\textless{}{-}} \FunctionTok{range}\NormalTok{(df\_scores}\SpecialCharTok{$}\NormalTok{boxcox)}
\NormalTok{df\_scores}\SpecialCharTok{$}\NormalTok{boxcox }\OtherTok{\textless{}{-}}\NormalTok{ scales}\SpecialCharTok{::}\FunctionTok{rescale}\NormalTok{(df\_scores}\SpecialCharTok{$}\NormalTok{boxcox, }\AttributeTok{to =} \FunctionTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{1}\NormalTok{))}
\CommentTok{\# Rescale SCL}
\NormalTok{df\_scores}\SpecialCharTok{$}\NormalTok{scl }\OtherTok{\textless{}{-}}\NormalTok{ scales}\SpecialCharTok{::}\FunctionTok{rescale}\NormalTok{(df\_scores}\SpecialCharTok{$}\NormalTok{scl, }\AttributeTok{to =} \FunctionTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{1}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Make plot data}
\NormalTok{df\_plot }\OtherTok{\textless{}{-}} \FunctionTok{do.call}\NormalTok{(rbind, }\FunctionTok{lapply}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\StringTok{"scl"}\NormalTok{, }\StringTok{"log"}\NormalTok{, }\StringTok{"sqrt"}\NormalTok{, }\StringTok{"qrt"}\NormalTok{, }\StringTok{"boxcox"}\NormalTok{), }\ControlFlowTok{function}\NormalTok{(n)\{}
  \FunctionTok{data.frame}\NormalTok{(df\_scores[}\FunctionTok{c}\NormalTok{(}\StringTok{"time"}\NormalTok{, }\StringTok{"id"}\NormalTok{)],}
             \AttributeTok{Value =}\NormalTok{ df\_scores[[n]],}
             \AttributeTok{Transformation =}\NormalTok{ n)}
\NormalTok{\}))}
\CommentTok{\# Plot}
\FunctionTok{ggplot}\NormalTok{(df\_plot, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ Value, }\AttributeTok{colour =}\NormalTok{ Transformation)) }\SpecialCharTok{+}
  \FunctionTok{geom\_density}\NormalTok{() }\SpecialCharTok{+}
  \FunctionTok{facet\_wrap}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{time) }\SpecialCharTok{+}
  \FunctionTok{scale\_y\_sqrt}\NormalTok{() }\SpecialCharTok{+}
  \FunctionTok{xlab}\NormalTok{(}\StringTok{"scl (rescaled to 0{-}1)"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{theme\_bw}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{dat }\OtherTok{\textless{}{-}}\NormalTok{ df\_scores[, }\FunctionTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"time"}\NormalTok{, }\StringTok{"boxcox"}\NormalTok{)]}
\NormalTok{dat }\OtherTok{\textless{}{-}} \FunctionTok{reshape}\NormalTok{(dat, }\AttributeTok{direction =} \StringTok{"wide"}\NormalTok{, }\AttributeTok{v.names =} \StringTok{"boxcox"}\NormalTok{, }\AttributeTok{timevar =} \StringTok{"time"}\NormalTok{, }\AttributeTok{idvar =} \StringTok{"id"}\NormalTok{)}
\FunctionTok{names}\NormalTok{(dat) }\OtherTok{\textless{}{-}} \FunctionTok{gsub}\NormalTok{(}\StringTok{"boxcox."}\NormalTok{, }\StringTok{"scl"}\NormalTok{, }\FunctionTok{names}\NormalTok{(dat))}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{set.seed}\NormalTok{(}\DecValTok{27796}\NormalTok{)}
\NormalTok{dat[[}\StringTok{"id"}\NormalTok{]] }\OtherTok{\textless{}{-}} \ConstantTok{NULL}
\NormalTok{res\_step }\OtherTok{\textless{}{-}} \FunctionTok{mx\_growth\_mixture}\NormalTok{(}
  \AttributeTok{model =}
  \StringTok{"}
\StringTok{  i =\textasciitilde{} 1*scl1 + 1*scl2 + 1*scl3 +1*scl4 +1*scl5 +1*scl6}
\StringTok{  step =\textasciitilde{} 0*scl1 + 1*scl2 + 1*scl3 +1*scl4 +1*scl5 +1*scl6}
\StringTok{  s =\textasciitilde{} 0*scl1 + 0*scl2 + 1*scl3 +2*scl4 +3*scl5 +4*scl6}
\StringTok{  scl1 \textasciitilde{}\textasciitilde{} vscl1*scl1}
\StringTok{  scl2 \textasciitilde{}\textasciitilde{} vscl2*scl2}
\StringTok{  scl3 \textasciitilde{}\textasciitilde{} vscl3*scl3}
\StringTok{  scl4 \textasciitilde{}\textasciitilde{} vscl4*scl4}
\StringTok{  scl5 \textasciitilde{}\textasciitilde{} vscl5*scl5}
\StringTok{  scl6 \textasciitilde{}\textasciitilde{} vscl6*scl6}
\StringTok{  i \textasciitilde{}\textasciitilde{} 0*i}
\StringTok{  step \textasciitilde{}\textasciitilde{} 0*step}
\StringTok{  s \textasciitilde{}\textasciitilde{} 0*s}
\StringTok{  i \textasciitilde{}\textasciitilde{} 0*s}
\StringTok{  i \textasciitilde{}\textasciitilde{} 0*step}
\StringTok{  s \textasciitilde{}\textasciitilde{} 0*step"}\NormalTok{, }\AttributeTok{classes =} \DecValTok{1}\SpecialCharTok{:}\DecValTok{5}\NormalTok{,}
  \AttributeTok{data =}\NormalTok{ dat)}
\CommentTok{\# Additional iterations because of}
\CommentTok{\# convergence problems for model 1:}
\NormalTok{res\_step[[}\DecValTok{1}\NormalTok{]] }\OtherTok{\textless{}{-}} \FunctionTok{mxTryHardWideSearch}\NormalTok{(res\_step[[}\DecValTok{1}\NormalTok{]], }\AttributeTok{extraTries =} \DecValTok{50}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Get fit table fit}
\NormalTok{tab\_fit }\OtherTok{\textless{}{-}} \FunctionTok{table\_fit}\NormalTok{(res\_step)}
\CommentTok{\# Select columns}
\NormalTok{tab\_fit }\OtherTok{\textless{}{-}}\NormalTok{ tab\_fit[, }\FunctionTok{c}\NormalTok{(}\StringTok{"Name"}\NormalTok{, }\StringTok{"Classes"}\NormalTok{, }\StringTok{"LL"}\NormalTok{, }\StringTok{"Parameters"}\NormalTok{, }\StringTok{"BIC"}\NormalTok{, }\StringTok{"Entropy"}\NormalTok{, }\StringTok{"prob\_min"}\NormalTok{, }\StringTok{"n\_min"}\NormalTok{, }\StringTok{"warning"}\NormalTok{, }\StringTok{"lmr\_p"}\NormalTok{)]}
\NormalTok{tab\_fit}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{res\_final }\OtherTok{\textless{}{-}} \FunctionTok{mx\_switch\_labels}\NormalTok{(res\_step[[}\DecValTok{3}\NormalTok{]], }\AttributeTok{param =} \StringTok{"M[1,7]"}\NormalTok{, }\AttributeTok{decreasing =} \ConstantTok{FALSE}\NormalTok{)}
\NormalTok{tab\_res }\OtherTok{\textless{}{-}} \FunctionTok{table\_results}\NormalTok{(res\_final, }\AttributeTok{columns =} \ConstantTok{NULL}\NormalTok{)}
\CommentTok{\# Select rows and columns}
\NormalTok{tab\_res }\OtherTok{\textless{}{-}}\NormalTok{ tab\_res[tab\_res}\SpecialCharTok{$}\NormalTok{Category }\SpecialCharTok{\%in\%} \FunctionTok{c}\NormalTok{(}\StringTok{"Means"}\NormalTok{, }\StringTok{"Variances"}\NormalTok{), }\FunctionTok{c}\NormalTok{(}\StringTok{"Category"}\NormalTok{, }\StringTok{"lhs"}\NormalTok{, }\StringTok{"est"}\NormalTok{, }\StringTok{"se"}\NormalTok{, }\StringTok{"pval"}\NormalTok{, }\StringTok{"confint"}\NormalTok{, }\StringTok{"name"}\NormalTok{)]}
\NormalTok{tab\_res}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{wald\_tests }\OtherTok{\textless{}{-}} \FunctionTok{wald\_test}\NormalTok{(res\_final, }
                   \StringTok{"}
\StringTok{                   class1.M[1,7] = class2.M[1,7]\&}
\StringTok{                   class1.M[1,7] = class3.M[1,7];}
\StringTok{                   class1.M[1,8] = class2.M[1,8]\&}
\StringTok{                   class1.M[1,8] = class3.M[1,8];}
\StringTok{                   class1.M[1,9] = class2.M[1,9]\&}
\StringTok{                   class1.M[1,9] = class3.M[1,9]"}\NormalTok{)}
\CommentTok{\# Rename the hypothesis}
\NormalTok{wald\_tests}\SpecialCharTok{$}\NormalTok{Hypothesis }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"Mean i"}\NormalTok{, }\StringTok{"Mean step"}\NormalTok{, }\StringTok{"Mean slope"}\NormalTok{)}
\NormalTok{papaja}\SpecialCharTok{::}\FunctionTok{apa\_table}\NormalTok{(wald\_tests, }\AttributeTok{digits =} \DecValTok{2}\NormalTok{, }\AttributeTok{caption =} \StringTok{"Wald tests"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{p }\OtherTok{\textless{}{-}} \FunctionTok{plot\_growth}\NormalTok{(res\_step[[}\DecValTok{3}\NormalTok{]], }\AttributeTok{rawdata =} \ConstantTok{TRUE}\NormalTok{, }\AttributeTok{alpha\_range =} \FunctionTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, .}\DecValTok{05}\NormalTok{))}
\CommentTok{\# Add Y{-}axis breaks in original scale}
\NormalTok{brks }\OtherTok{\textless{}{-}} \FunctionTok{seq}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{1}\NormalTok{, }\AttributeTok{length.out =} \DecValTok{5}\NormalTok{)}
\NormalTok{labs }\OtherTok{\textless{}{-}} \FunctionTok{round}\NormalTok{(}\FunctionTok{invbc}\NormalTok{(scales}\SpecialCharTok{::}\FunctionTok{rescale}\NormalTok{(brks, }\AttributeTok{from =} \FunctionTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{1}\NormalTok{), }\AttributeTok{to =}\NormalTok{ rng\_bc), lambda))}
\NormalTok{p }\OtherTok{\textless{}{-}}\NormalTok{ p }\SpecialCharTok{+} \FunctionTok{scale\_y\_continuous}\NormalTok{(}\AttributeTok{breaks =} \FunctionTok{seq}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{1}\NormalTok{, }\AttributeTok{length.out =} \DecValTok{5}\NormalTok{), }\AttributeTok{labels =}\NormalTok{ labs) }\SpecialCharTok{+} \FunctionTok{ylab}\NormalTok{(}\StringTok{"SCL (rescaled from Box{-}Cox)"}\NormalTok{)}
\NormalTok{p}
\end{Highlighting}
\end{Shaded}

@@

\hypertarget{r-session}{%
\subsection{R session}\label{r-session}}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{sessionInfo}\NormalTok{()}
\CommentTok{\#\textgreater{} R version 4.1.3 (2022{-}03{-}10)}
\CommentTok{\#\textgreater{} Platform: x86\_64{-}w64{-}mingw32/x64 (64{-}bit)}
\CommentTok{\#\textgreater{} Running under: Windows 10 x64 (build 19045)}
\CommentTok{\#\textgreater{} }
\CommentTok{\#\textgreater{} Matrix products: default}
\CommentTok{\#\textgreater{} }
\CommentTok{\#\textgreater{} locale:}

>>>>

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{df\_scores }\OtherTok{\textless{}{-}}\NormalTok{ df\_plot}
\CommentTok{\# Store original range of SCL}
\NormalTok{rng\_scl }\OtherTok{\textless{}{-}} \FunctionTok{range}\NormalTok{(df\_scores}\SpecialCharTok{$}\NormalTok{scl)}
\CommentTok{\# Log{-}transform}
\NormalTok{df\_scores}\SpecialCharTok{$}\NormalTok{log }\OtherTok{\textless{}{-}}\NormalTok{ scales}\SpecialCharTok{::}\FunctionTok{rescale}\NormalTok{(}\FunctionTok{log}\NormalTok{(df\_scores}\SpecialCharTok{$}\NormalTok{scl), }\AttributeTok{to =} \FunctionTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{,}
    \DecValTok{1}\NormalTok{))}
\CommentTok{\# Square root transform}
\NormalTok{df\_scores}\SpecialCharTok{$}\NormalTok{sqrt }\OtherTok{\textless{}{-}}\NormalTok{ scales}\SpecialCharTok{::}\FunctionTok{rescale}\NormalTok{(}\FunctionTok{sqrt}\NormalTok{(df\_scores}\SpecialCharTok{$}\NormalTok{scl), }\AttributeTok{to =} \FunctionTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{,}
    \DecValTok{1}\NormalTok{))}
\CommentTok{\# Cube root transform}
\NormalTok{df\_scores}\SpecialCharTok{$}\NormalTok{qrt }\OtherTok{\textless{}{-}}\NormalTok{ scales}\SpecialCharTok{::}\FunctionTok{rescale}\NormalTok{(df\_scores}\SpecialCharTok{$}\NormalTok{scl}\SpecialCharTok{\^{}}\FloatTok{0.33}\NormalTok{, }\AttributeTok{to =} \FunctionTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{,}
    \DecValTok{1}\NormalTok{))}
\CommentTok{\# Reciprocal transform}
\NormalTok{df\_scores}\SpecialCharTok{$}\NormalTok{reciprocal }\OtherTok{\textless{}{-}}\NormalTok{ scales}\SpecialCharTok{::}\FunctionTok{rescale}\NormalTok{(}\DecValTok{1}\SpecialCharTok{/}\NormalTok{df\_scores}\SpecialCharTok{$}\NormalTok{scl, }\AttributeTok{to =} \FunctionTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{,}
    \DecValTok{1}\NormalTok{))}
\CommentTok{\# Define function for Box{-}Cox transformation}
\NormalTok{bc }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(x, lambda) \{}
\NormalTok{    (((x}\SpecialCharTok{\^{}}\NormalTok{lambda) }\SpecialCharTok{{-}} \DecValTok{1}\NormalTok{)}\SpecialCharTok{/}\NormalTok{lambda)}
\NormalTok{\}}
\CommentTok{\# Inverse Box{-}Cox transformation}
\NormalTok{invbc }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(x, lambda) \{}
\NormalTok{    ((x }\SpecialCharTok{*}\NormalTok{ lambda) }\SpecialCharTok{+} \DecValTok{1}\NormalTok{)}\SpecialCharTok{\^{}}\NormalTok{(}\DecValTok{1}\SpecialCharTok{/}\NormalTok{lambda)}
\NormalTok{\}}
\CommentTok{\# Box{-}Cox transform}
\NormalTok{b }\OtherTok{\textless{}{-}}\NormalTok{ MASS}\SpecialCharTok{::}\FunctionTok{boxcox}\NormalTok{(}\FunctionTok{lm}\NormalTok{(df\_scores}\SpecialCharTok{$}\NormalTok{scl }\SpecialCharTok{\textasciitilde{}} \DecValTok{1}\NormalTok{), }\AttributeTok{plotit =} \ConstantTok{FALSE}\NormalTok{)}
\NormalTok{lambda }\OtherTok{\textless{}{-}}\NormalTok{ b}\SpecialCharTok{$}\NormalTok{x[}\FunctionTok{which.max}\NormalTok{(b}\SpecialCharTok{$}\NormalTok{y)]}
\NormalTok{df\_scores}\SpecialCharTok{$}\NormalTok{boxcox }\OtherTok{\textless{}{-}} \FunctionTok{bc}\NormalTok{(df\_scores}\SpecialCharTok{$}\NormalTok{scl, lambda)}
\CommentTok{\# Store range of Box{-}Cox transformed data}
\NormalTok{rng\_bc }\OtherTok{\textless{}{-}} \FunctionTok{range}\NormalTok{(df\_scores}\SpecialCharTok{$}\NormalTok{boxcox)}
\NormalTok{df\_scores}\SpecialCharTok{$}\NormalTok{boxcox }\OtherTok{\textless{}{-}}\NormalTok{ scales}\SpecialCharTok{::}\FunctionTok{rescale}\NormalTok{(df\_scores}\SpecialCharTok{$}\NormalTok{boxcox, }\AttributeTok{to =} \FunctionTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{,}
    \DecValTok{1}\NormalTok{))}
\CommentTok{\# Rescale SCL}
\NormalTok{df\_scores}\SpecialCharTok{$}\NormalTok{scl }\OtherTok{\textless{}{-}}\NormalTok{ scales}\SpecialCharTok{::}\FunctionTok{rescale}\NormalTok{(df\_scores}\SpecialCharTok{$}\NormalTok{scl, }\AttributeTok{to =} \FunctionTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{1}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Make plot data}
\NormalTok{df\_plot }\OtherTok{\textless{}{-}} \FunctionTok{do.call}\NormalTok{(rbind, }\FunctionTok{lapply}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\StringTok{"scl"}\NormalTok{, }\StringTok{"log"}\NormalTok{, }\StringTok{"sqrt"}\NormalTok{, }\StringTok{"qrt"}\NormalTok{,}
    \StringTok{"boxcox"}\NormalTok{), }\ControlFlowTok{function}\NormalTok{(n) \{}
    \FunctionTok{data.frame}\NormalTok{(df\_scores[}\FunctionTok{c}\NormalTok{(}\StringTok{"time"}\NormalTok{, }\StringTok{"id"}\NormalTok{)], }\AttributeTok{Value =}\NormalTok{ df\_scores[[n]],}
        \AttributeTok{Transformation =}\NormalTok{ n)}
\NormalTok{\}))}
\CommentTok{\# Plot}
\FunctionTok{ggplot}\NormalTok{(df\_plot, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ Value, }\AttributeTok{colour =}\NormalTok{ Transformation)) }\SpecialCharTok{+} \FunctionTok{geom\_density}\NormalTok{() }\SpecialCharTok{+}
    \FunctionTok{facet\_wrap}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{time) }\SpecialCharTok{+} \FunctionTok{scale\_y\_sqrt}\NormalTok{() }\SpecialCharTok{+} \FunctionTok{xlab}\NormalTok{(}\StringTok{"scl (rescaled to 0{-}1)"}\NormalTok{) }\SpecialCharTok{+}
    \FunctionTok{theme\_bw}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{dat }\OtherTok{\textless{}{-}}\NormalTok{ df\_scores[, }\FunctionTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"time"}\NormalTok{, }\StringTok{"boxcox"}\NormalTok{)]}
\NormalTok{dat }\OtherTok{\textless{}{-}} \FunctionTok{reshape}\NormalTok{(dat, }\AttributeTok{direction =} \StringTok{"wide"}\NormalTok{, }\AttributeTok{v.names =} \StringTok{"boxcox"}\NormalTok{, }\AttributeTok{timevar =} \StringTok{"time"}\NormalTok{,}
    \AttributeTok{idvar =} \StringTok{"id"}\NormalTok{)}
\FunctionTok{names}\NormalTok{(dat) }\OtherTok{\textless{}{-}} \FunctionTok{gsub}\NormalTok{(}\StringTok{"boxcox."}\NormalTok{, }\StringTok{"scl"}\NormalTok{, }\FunctionTok{names}\NormalTok{(dat))}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{set.seed}\NormalTok{(}\DecValTok{27796}\NormalTok{)}
\NormalTok{dat[[}\StringTok{"id"}\NormalTok{]] }\OtherTok{\textless{}{-}} \ConstantTok{NULL}
\NormalTok{res\_step }\OtherTok{\textless{}{-}} \FunctionTok{mx\_growth\_mixture}\NormalTok{(}\AttributeTok{model =} \StringTok{"}
\StringTok{  i =\textasciitilde{} 1*scl1 + 1*scl2 + 1*scl3 +1*scl4 +1*scl5 +1*scl6}
\StringTok{  step =\textasciitilde{} 0*scl1 + 1*scl2 + 1*scl3 +1*scl4 +1*scl5 +1*scl6}
\StringTok{  s =\textasciitilde{} 0*scl1 + 0*scl2 + 1*scl3 +2*scl4 +3*scl5 +4*scl6}
\StringTok{  scl1 \textasciitilde{}\textasciitilde{} vscl1*scl1}
\StringTok{  scl2 \textasciitilde{}\textasciitilde{} vscl2*scl2}
\StringTok{  scl3 \textasciitilde{}\textasciitilde{} vscl3*scl3}
\StringTok{  scl4 \textasciitilde{}\textasciitilde{} vscl4*scl4}
\StringTok{  scl5 \textasciitilde{}\textasciitilde{} vscl5*scl5}
\StringTok{  scl6 \textasciitilde{}\textasciitilde{} vscl6*scl6}
\StringTok{  i \textasciitilde{}\textasciitilde{} 0*i}
\StringTok{  step \textasciitilde{}\textasciitilde{} 0*step}
\StringTok{  s \textasciitilde{}\textasciitilde{} 0*s}
\StringTok{  i \textasciitilde{}\textasciitilde{} 0*s}
\StringTok{  i \textasciitilde{}\textasciitilde{} 0*step}
\StringTok{  s \textasciitilde{}\textasciitilde{} 0*step"}\NormalTok{,}
    \AttributeTok{classes =} \DecValTok{1}\SpecialCharTok{:}\DecValTok{5}\NormalTok{, }\AttributeTok{data =}\NormalTok{ dat)}
\CommentTok{\# Additional iterations because of convergence problems for}
\CommentTok{\# model 1:}
\NormalTok{res\_step[[}\DecValTok{1}\NormalTok{]] }\OtherTok{\textless{}{-}} \FunctionTok{mxTryHardWideSearch}\NormalTok{(res\_step[[}\DecValTok{1}\NormalTok{]], }\AttributeTok{extraTries =} \DecValTok{50}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Get fit table fit}
\NormalTok{tab\_fit }\OtherTok{\textless{}{-}} \FunctionTok{table\_fit}\NormalTok{(res\_step)}
\CommentTok{\# Select columns}
\NormalTok{tab\_fit }\OtherTok{\textless{}{-}}\NormalTok{ tab\_fit[, }\FunctionTok{c}\NormalTok{(}\StringTok{"Name"}\NormalTok{, }\StringTok{"Classes"}\NormalTok{, }\StringTok{"LL"}\NormalTok{, }\StringTok{"Parameters"}\NormalTok{,}
    \StringTok{"BIC"}\NormalTok{, }\StringTok{"Entropy"}\NormalTok{, }\StringTok{"prob\_min"}\NormalTok{, }\StringTok{"n\_min"}\NormalTok{, }\StringTok{"warning"}\NormalTok{, }\StringTok{"lmr\_p"}\NormalTok{)]}
\NormalTok{tab\_fit}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{res\_final }\OtherTok{\textless{}{-}} \FunctionTok{mx\_switch\_labels}\NormalTok{(res\_step[[}\DecValTok{3}\NormalTok{]], }\AttributeTok{param =} \StringTok{"M[1,7]"}\NormalTok{,}
    \AttributeTok{decreasing =} \ConstantTok{FALSE}\NormalTok{)}
\NormalTok{tab\_res }\OtherTok{\textless{}{-}} \FunctionTok{table\_results}\NormalTok{(res\_final, }\AttributeTok{columns =} \ConstantTok{NULL}\NormalTok{)}
\CommentTok{\# Select rows and columns}
\NormalTok{tab\_res }\OtherTok{\textless{}{-}}\NormalTok{ tab\_res[tab\_res}\SpecialCharTok{$}\NormalTok{Category }\SpecialCharTok{\%in\%} \FunctionTok{c}\NormalTok{(}\StringTok{"Means"}\NormalTok{, }\StringTok{"Variances"}\NormalTok{),}
    \FunctionTok{c}\NormalTok{(}\StringTok{"Category"}\NormalTok{, }\StringTok{"lhs"}\NormalTok{, }\StringTok{"est"}\NormalTok{, }\StringTok{"se"}\NormalTok{, }\StringTok{"pval"}\NormalTok{, }\StringTok{"confint"}\NormalTok{, }\StringTok{"name"}\NormalTok{)]}
\NormalTok{tab\_res}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{wald\_tests }\OtherTok{\textless{}{-}} \FunctionTok{wald\_test}\NormalTok{(res\_final, }\StringTok{"}
\StringTok{                   class1.M[1,7] = class2.M[1,7]\&}
\StringTok{                   class1.M[1,7] = class3.M[1,7];}
\StringTok{                   class1.M[1,8] = class2.M[1,8]\&}
\StringTok{                   class1.M[1,8] = class3.M[1,8];}
\StringTok{                   class1.M[1,9] = class2.M[1,9]\&}
\StringTok{                   class1.M[1,9] = class3.M[1,9]"}\NormalTok{)}
\CommentTok{\# Rename the hypothesis}
\NormalTok{wald\_tests}\SpecialCharTok{$}\NormalTok{Hypothesis }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"Mean i"}\NormalTok{, }\StringTok{"Mean step"}\NormalTok{, }\StringTok{"Mean slope"}\NormalTok{)}
\NormalTok{papaja}\SpecialCharTok{::}\FunctionTok{apa\_table}\NormalTok{(wald\_tests, }\AttributeTok{digits =} \DecValTok{2}\NormalTok{, }\AttributeTok{caption =} \StringTok{"Wald tests"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{p }\OtherTok{\textless{}{-}} \FunctionTok{plot\_growth}\NormalTok{(res\_step[[}\DecValTok{3}\NormalTok{]], }\AttributeTok{rawdata =} \ConstantTok{TRUE}\NormalTok{, }\AttributeTok{alpha\_range =} \FunctionTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{,}
    \FloatTok{0.05}\NormalTok{))}
\CommentTok{\# Add Y{-}axis breaks in original scale}
\NormalTok{brks }\OtherTok{\textless{}{-}} \FunctionTok{seq}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{1}\NormalTok{, }\AttributeTok{length.out =} \DecValTok{5}\NormalTok{)}
\NormalTok{labs }\OtherTok{\textless{}{-}} \FunctionTok{round}\NormalTok{(}\FunctionTok{invbc}\NormalTok{(scales}\SpecialCharTok{::}\FunctionTok{rescale}\NormalTok{(brks, }\AttributeTok{from =} \FunctionTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{1}\NormalTok{), }\AttributeTok{to =}\NormalTok{ rng\_bc),}
\NormalTok{    lambda))}
\NormalTok{p }\OtherTok{\textless{}{-}}\NormalTok{ p }\SpecialCharTok{+} \FunctionTok{scale\_y\_continuous}\NormalTok{(}\AttributeTok{breaks =} \FunctionTok{seq}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{1}\NormalTok{, }\AttributeTok{length.out =} \DecValTok{5}\NormalTok{),}
    \AttributeTok{labels =}\NormalTok{ labs) }\SpecialCharTok{+} \FunctionTok{ylab}\NormalTok{(}\StringTok{"SCL (rescaled from Box{-}Cox)"}\NormalTok{)}
\NormalTok{p}
\end{Highlighting}
\end{Shaded}

@@
